%%
%% ICDCS 2026 Submission - DeepVis
%%
\documentclass[conference]{IEEEtran}

%% Packages
\usepackage{amsmath}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{pifont}
\usepackage[caption=false]{subfig}  % IEEEtran compatible
\usepackage{float}
\usepackage{url}
\usepackage{array}
\usepackage{booktabs}
% \usepackage[disable]{todonotes} % Removed to eliminate warning
\usepackage{tikz}
\usetikzlibrary{fit,shapes,arrows,positioning}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{xcolor}
\usepackage{colortbl}

%% Commands
\newcommand{\DeepVis}{\texttt{DeepVis}\xspace}
% Colored checkmarks and X marks for tables
\newcommand{\cmark}{{\color{green!70!black}\ding{51}}}  % Green checkmark
\newcommand{\xmark}{{\color{red!80!black}\ding{55}}}    % Red X mark
\newcommand{\pmark}{{\color{orange!80!black}$\triangle$}} % Orange partial

\begin{document}

\title{DeepVis: Deep Learning-Based File System Fingerprinting for Cloud Security}

%% Anonymous author block for double-blind review
\author{}

\maketitle

\begin{abstract}
This paper presents \DeepVis, a high-throughput integrity verification system designed to act as a first-pass triage filter for extreme-scale storage environments such as cloud data centers.
Our key idea is to leverage a spatial hash projection architecture, enabling highly parallelized metadata processing while maintaining detection accuracy via a stable tensor representation.
Specifically, \DeepVis first introduces an asynchronous snapshot engine that leverages high-performance I/O interfaces to maximize ingestion rates, allowing the system to rapidly capture file system states.
Second, \DeepVis devises a lock-free tensor mapping pipeline, where metadata processing is sharded across processor cores to eliminate contention and achieve linear scalability.
Finally, \DeepVis adopts a spatial anomaly detection approach, enabling the identification of sparse attack signals even amidst significant background noise caused by legitimate system updates.
We evaluate \DeepVis on production-grade cloud infrastructure. Our results show that \DeepVis acts as an effective \textit{snapshot-based audit system}, detecting 97.1\% of hidden kernel modules and packed binaries in Linux environments. By achieving a 10.9$\times$ speedup over traditional FIM, \DeepVis enables frequent, full-system verification intervals, eliminating the reliance on potentially unreliable incremental event streams (e.g., fanotify).
\end{abstract}

\begin{IEEEkeywords}
Distributed Systems, File System Monitoring, Scalable Verification, Anomaly Detection, Spatial Representation Learning
\end{IEEEkeywords}

\input{1. Introduction.tex}
\input{2. Background.tex}
\input{3. Design.tex}
\input{4. Evaluation.tex}
\input{5. Related Works.tex}
\input{6. Discussion and Limitation.tex}
\input{7. Conclusion.tex}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
